### 2018-03-10 paper/build.tex
Add TODOs for Neil

The build function takes 4 type arguments: \hs{c} is the constraint used for \hs{Compute} (typically either \hs{Applicative} or \hs{Monad}), \hs{i} is the information stored by the build system and \hs{k}/\hs{v} are the key/value types as described in \S\ref{todo}. Given a build system \hs{build}:

@@

@@

If the \hs{Compute} function for \hs{k} calls the functional argument of \hs{d} then the build system is responsible for ensuring that \hs{d} is built \textit{before} \hs{k}. Looking at the build systems in \S\ref{todo} we have observed 3 distinct approaches to respecting dependency orderings. In this section of the paper we'll explore what properties are a consequence and how they operate.

@@

@@

@@

>>>>

The build function takes 4 type arguments: \hs{c} is the constraint used for \hs{Compute} (typically either \hs{Applicative} or \hs{Monad}), \hs{i} is the information stored by the build system and \hs{k}/\hs{v} are the key/value types as described in \S\ref{sec-vocabulary}. Given a build system \hs{build}:

@@

\todo{NM}{We haven't used the term `target' before, perhaps change to `keys'?}

@@

If the \hs{Compute} function for \hs{k} calls the functional argument of \hs{d} then the build system is responsible for ensuring that \hs{d} is built \textit{before} \hs{k}. Looking at the build systems in \S\ref{sec-background} we have observed 3 distinct approaches to respecting dependency orderings. In this section of the paper we'll explore what properties are a consequence and how they operate.

@@

\todo{NM}{In this case we can give actual code, so let's do that?}

@@

\todo{NM}{I found terms `predicate' and `generative' hard to grasp and a bit abstract. Especially `predicate'.}

\todo{NM}{I would also like to see an actual \hs{upToDate} function for predicate, and a \hs{recover}/\hs{fetch} or something like that for generative.}

@@

\todo{NM}{This sounds very interesting, but I didn't get it after a quick read, and it's late. I think we need examples for all these cases, ideally reusing the examples from the background section.}

\todo{NM}{I'm becoming a bit more optimistic about the term `trace'. It sounds conceptually simpler than a `dependency graph' even though it's isomorphic. So, let's keep it, with a note somewhere, pointing out that traces actually contain enough information to recover dependency graphs.}
